$\pi$ with leftovers: \\ a mechanisation in Agda

### 2020-05-01 paper/paper.tex
pass on os

\autoref{fig:reduction} models the operational semantics of the \picalc{}.
Processes put in parallel reduce when they communicate over a common channel.
The receiving process substitutes references to its most immediate variable with references to the variable that is being sent by the process doing the output.
The process is then \emph{lowered} --- all variable references are decreased by one.
Reduction is closed under structural congruence and goes under parallel composition and scope restriction
--- notably, not under input nor output, or otherwise the sequencing of actions would not be preserved.
In  \autoref{subject-reduction} we prove that if $P$ reduces to $Q$ and $P$ is well-typed, so is $Q$.
However, this reduction operation is effectful: it consumes the channel over which communication occurs.
If this channel is external to $P$ (it resides in its context) then the context in which $Q$ is typed must change.
To keep track of this information, we lift the index of the channel to the type level.
We use a $dec$ function to decrement the index of the channel every time we come out of a binder.
This function saturates at $\constr{internal}$ --- meaning communication happens internally to the process.

>>>>

The operational semantics of the \picalc{} is defined via a reduction relation in \autoref{fig:reduction}.
In rule $\constr{comm}$, processes in parallel reduce when they communicate over the same index ${i}$.
The input process $\recv{i}P$ substitutes in $P$ references to the most immediate variable placeholder with references to the variable sent by the output process $\send{i}{j}{Q}$.
The continuation $\subst{P}{j}{0}$ is then \emph{lowered} --- all variable references are decreased by one.
Reduction is closed under parallel composition (rule $\constr{par}$), scope restriction (rule $\constr{res}$) and structural congruence (rule $\constr{struct}$) 
--- notably, not under input nor output, otherwise the sequencing of actions would not be preserved \cite{Sangio01}.
%In  \autoref{subject-reduction} we prove that if $P$ reduces to $Q$ and $P$ is well-typed, so is $Q$.

\todo{this paragraph below is not clear}
Notice that the reduction relation in \autoref{fig:reduction} is effectful: it consumes the channel over which communication occurs.
If the channel is external to $P$ (it resides in its context) then the context in which $Q$ is typed must change.
To keep track of this information, we lift the index of the channel to the type level.
We use a $dec$ function to decrement the index of the channel every time we come out of a binder.
This function saturates at $\constr{internal}$ --- meaning communication happens internally to the process.
